### 2021-01-10 tex/final-presentation.tex
Add final presentation.
Add some slides.

\date{\formatdate{20}{10}{2020}}

@@

  \begin{frame}{Outline}
    \begin{itemize}
      \item Motivation
      \item Low-Code Architecture
      \item Model-Driven Architecture
      \item Criticisms
      \item Planned Project Procedure
    \end{itemize}
  \end{frame}

@@

  \begin{frame}{Planned Project Procedure}
    \begin{itemize}
      \item Evaluate a set of Low-Code tools.
      \item Evaluate a set of Model-Driven tools.
      \item For each tool, determine what it can and can't do.
      \item Compare the two sets with each other and draw some conclusions.
    \end{itemize}
  \end{frame}
\end{document}

>>>>

\date{\formatdate{12}{01}{2021}}

@@

  \begin{frame}{Outline}
    \begin{itemize}
      \item Motivation
      \item Model-Driven Architecture
      \item Low-Code Architecture
      \item Criticisms
      \item Planned Project Procedure
    \end{itemize}
  \end{frame}

@@

  \begin{frame}{Evaluation of Low-Code Tools}
    \begin{itemize}
      \item Find low-code tools in the following categories:
          \begin{itemize}
            \item open-source
            \item developed by well-known company
            \item developed by unknown company
            \item old/well-established platform
            \item new/unestablished
          \end{itemize}
      \item Set up each tool
      \item Build test application with each tool
    \end{itemize}
  \end{frame}

  \begin{frame}{Open Standard Business Platform (OBSP)}
    \begin{itemize}
      \item open-source
      \item plug-in for the Eclipse IDE
      \item community version of the commercial OS.bee product developed by COMPEX
      \item latest version over one year old
      \item does not work with latest version of the Eclipse IDE
    \end{itemize}
  \end{frame}

  \begin{frame}{Corteza Low Code}
    \begin{itemize}
      \item open-source
      \item part of the Corteza Project initiated by Crust Technology
      \item the Corteza Project includes a CRM solution built on top of Corteza~Low~Code, among other things
      \item web-based platform
      \item test by signing up with a GitHub or Google account or \\
            by deploying it locally using Docker
    \end{itemize}
  \end{frame}

  \begin{frame}{Oracle APEX (Application Express)}
    \begin{itemize}
      \item commercial
      \item initially released as Oracle Flows in 2000
      \item web-based platform
      \item test by signing up for an Oracle Cloud account or \\
            by requesting an APEX workspace
    \end{itemize}
  \end{frame}

  \begin{frame}{Simplifier}
    \begin{itemize}
      \item commercial
      \item initially released by iTiZZiMO in 2012
      \item web-based platform
      \item test by using the Simplifier Playground (data is wiped every day) or \\
            by requesting a Simplifier test instance
    \end{itemize}
  \end{frame}

  \begin{frame}{Mendix}
    \begin{itemize}
      \item commercial
      \item founded in 2005 as a subsidiary of Siemens
      \item web-based platform (Mendix Studio) and Windows application \\
            (Mendix Studio Pro) with advanced features
      \item test by signing up for a regular account which allows hosting unlimited applications (with 1GB of memory and 0.5GB of storage per application)
    \end{itemize}
  \end{frame}
\end{document}
